HTLSDstack

### 2025-10-09 Code/R/Research/HTLSDstack.Rmd
code for precision research in different cases

```{r warning=FALSE}
# sd <- snr_to_sd(s, snr = 35)
out_len <- 16
sds <- seq(0, 1.5, length.out = out_len)
rmse_df <- data.frame(sd = sds, esprit = numeric(out_len), HTLSDstack = numeric(out_len),
                      tens1 = numeric(out_len), tens2 = numeric(out_len))
R <- 100
for (i in seq_along(sds)) {
  print(i)
  sd <- sds[i]
  with(plan(multisession), {
    batch_recs <- function(R) {
      p <- progressor(R)
      future_replicate(R, {
        p()
        compare_rec_r()
      }, simplify = "array", future.seed = 5)
    }
    if (sd == 1)
      recs <- batch_recs(2)
    else
      recs <- batch_recs(R)
  })

>>>>

```{r warning=FALSE}
# sd <- snr_to_sd(s, snr = 35)
out_len <- 16
sds <- seq(0, 1.5, length.out = out_len)
rmse_df <- data.frame(sd = sds, esprit = numeric(out_len), HTLSDstack = numeric(out_len),
                      tens1 = numeric(out_len), tens2 = numeric(out_len))
R <- 100
for (i in seq_along(sds)) {
  print(i)
  sd <- sds[i]
  with(plan(multisession), {
    batch_recs <- function(R) {
      p <- progressor(R)
      future_replicate(R, {
        p()
        compare_rec_r()
      }, simplify = "array", future.seed = 5)
    }
    if (sd == 0)
      recs <- batch_recs(2)
    else
      recs <- batch_recs(R)
  })
